\section{Introduction}
\label{intro}
The system should take audio as input and output acoustic audio by means of an high voltage electric discharge in air creating plasma by the means of a resonant transformer (tesla coil). The system should also be designed such that it will always be functional, and in the case of the system not being functional should fail in a safe and non-destructive way (safe having priority over non-destructive). As well as indicating witch part of the system is non-functional. The system should also be designed in such a way that this non-functioning part may be swapped for a spare functioning part.

\subsection{Tesla}
\label{tesla}
%http://www.tfcbooks.com/tesla/contents.htm
The Tesla Coil is a form of resonant transformer invented by Nikolai Tesla and used for experiments with artificial illumination \citep{5570149}. A resonant transformer consists of two inductively coupled coils, each loaded with a capacitance such that they get the same resonance frequencies. The resonant transformer has since gotten a lot of applications, among others; RFID, NFC, and Wireless charging.The resonant transformer in the form of the tesla coil has also become a popular entertainment device.
%Death ray
%Entertainment

\subsection{Version control}
All digital produced material have been stored in a central Git-based version control system. The main reason for using this is because the system remembers the history of all the files in the project. Then if something goes wrong, it is possible to get an earlier version back again. A version control system also make things easier to manage when several people are working together on the same project.